Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

\subsection{Link encoding as subgraphs union}
\label{sec:link}
Most methods for link prediction compute pairwise nodes similarities treating  the nodes defining the candidate edge independently. Instead we propose to jointly consider both candidate endpoint nodes together with their extended ''context''. To do so we build a graph starting from the two nodes and the underlying network. Given nodes $u$ and $v$, we first extract the two neighborhood sets with a user defined radius $R$ rooted at $u$ and $v$ to obtain $N_R(u)$ and $N_R(v)$, respectively. We then consider the graph $\mathcal{J}$ induced by the set union $N_R(u) \cup N_R(u)$. Finally we add an auxiliary node $w$ and the necessary edges to connect it to $u$ and $v$ (see Fig.\ref{fig:example}).
\begin{figure}
\centering
\includegraphics[height=2.2cm]{subgraphs}
\caption{Example of joint neighborhood subgraphs.}
\label{fig:example}
\end{figure}

@@

\hline
         & \multicolumn{6}{c|}{\textbf{Datasets}}\\
 \hline
\textbf{Methods} & Protein & Metabolic & Nips & Condmat & Conflict & PowerGrid\\
	& ($\%$) & ($\%$) & ($\%$) & ($\%$) & ($\%$) & ($\%$)\\
\hline
AA & 56.4$\pm$0.5 & 52.4$\pm$0.5 & 51.2$\pm$0.2 & 56.7$\pm$1.4 & 50.7$\pm$0.8 & 58.9$\pm$0.3\\
PA & 75.0$\pm$0.3 & 52.4$\pm$0.5 & 54.3$\pm$0.5 & 71.6$\pm$2.6 & 54.6$\pm$2.4 & 44.2$\pm$01.0\\
SHP & 72.6$\pm$0.5 & 62.6$\pm$0.4 & 51.7$\pm$0.3 & 67.3$\pm$1.8 & 51.2$\pm$1.4 & 65.9$\pm$1.5\\
Katz & 72.7$\pm$0.5 & 60.8$\pm$0.7 & 51.7$\pm$0.3 & 67.3$\pm$1.7 & 51.2$\pm$1.4 & 65.5$\pm$1.6 \\
Sup-Top & 75.4$\pm$0.3 & 62.8$\pm$0.1 & 54.2$\pm$0.7 & 72.0$\pm$2.0 & 69.5$\pm$7.6 & 70.8$\pm$6.2\\
SVD & 63.5$\pm$0.3 & 53.8$\pm$1.7 & 51.2$\pm$3.1 & 62.9$\pm$5.1 & 54.1$\pm$9.4 & 69.1$\pm$2.6\\
Fact+Scores & 79.3$\pm$0.5 & 69.6$\pm$0.2 & 61.3$\pm$1.9 & 81.2$\pm$2.0 & 68.9$\pm$4.2 & 75.1$\pm$2.0 \\
JNSL & \textbf{80.1$\pm$0.8} & \textbf{72.5$\pm$0.7} & \textbf{62.1$\pm$0.8} & \textbf{88.6$\pm$2.3} & \textbf{72.0$\pm$0.9} & \textbf{75.6$\pm$0.7} \\
 \hline 
\end{tabular}
\label{result_table}
\end{table}
\section{Conclusion and Future Work}
In this paper, we have proposed an effective method for link prediction. Our method takes advantages from the way to represent links as joint neighborhood subgraphs and the employment of an convolution kernel that is able to efficiently exploit the graph structure. The results from the experiment show that our method is the state of the art for graph structured link prediction, especially when the side information are not available.

For the future work, we plan to investigate to propose a method for link prediction which can make use of the variety of information sources associated with graphs.

>>>>

\subsection{Link encoding as subgraphs union}
\label{sec:link}
Most methods for link prediction compute pairwise nodes similarities treating  the nodes defining the candidate edge independently. Instead we propose to jointly consider both candidate endpoint nodes together with their extended ''context''. To do so we build a graph starting from the two nodes and the underlying network. Given nodes $u$ and $v$, we first extract the two neighborhood sets with a user defined radius $R$ rooted at $u$ and $v$ to obtain $N_R(u)$ and $N_R(v)$, respectively. We then consider the graph $\mathcal{J}$ induced by the set union $N_R(u) \cup N_R(u)$. Finally we add an auxiliary node $w$ and the necessary edges to connect it to $u$ and $v$ (see Fig.\ref{fig:example}).
\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{subgraphs}
\caption{Left) a given network. Right) joint neighborhood subgraphs for an existing (top) and a non existing link (bottom).}
\label{fig:example}
\end{figure}

@@

\hline
         & \multicolumn{6}{c|}{\textbf{Datasets}}\\
 \hline
\textbf{Methods} & Protein & Metabolic & Nips & Condmat & Conflict & PowerGrid\\
	& ($\%$) & ($\%$) & ($\%$) & ($\%$) & ($\%$) & ($\%$)\\
\hline
AA & 56.4$\pm$0.5 & 52.4$\pm$0.5 & 51.2$\pm$0.2 & 56.7$\pm$1.4 & 50.7$\pm$0.8 & 58.9$\pm$0.3\\
PA & 75.0$\pm$0.3 & 52.4$\pm$0.5 & 54.3$\pm$0.5 & 71.6$\pm$2.6 & 54.6$\pm$2.4 & 44.2$\pm$01.0\\
SHP & 72.6$\pm$0.5 & 62.6$\pm$0.4 & 51.7$\pm$0.3 & 67.3$\pm$1.8 & 51.2$\pm$1.4 & 65.9$\pm$1.5\\
Katz & 72.7$\pm$0.5 & 60.8$\pm$0.7 & 51.7$\pm$0.3 & 67.3$\pm$1.7 & 51.2$\pm$1.4 & 65.5$\pm$1.6 \\
Sup-Top & 75.4$\pm$0.3 & 62.8$\pm$0.1 & 54.2$\pm$0.7 & 72.0$\pm$2.0 & 69.5$\pm$7.6 & 70.8$\pm$6.2\\
SVD & 63.5$\pm$0.3 & 53.8$\pm$1.7 & 51.2$\pm$3.1 & 62.9$\pm$5.1 & 54.1$\pm$9.4 & 69.1$\pm$2.6\\
Fact+Scores & 79.3$\pm$0.5 & 69.6$\pm$0.2 & 61.3$\pm$1.9 & 81.2$\pm$2.0 & 68.9$\pm$4.2 & 75.1$\pm$2.0 \\
JNSL & \textbf{80.1$\pm$0.8} & \textbf{72.5$\pm$0.7} & \textbf{62.1$\pm$0.8} & \textbf{88.6$\pm$2.3} & \textbf{72.0$\pm$0.9} & \textbf{75.6$\pm$0.7} \\
 \hline 
\end{tabular}
\label{result_table}
\end{table}

\section{Conclusion and Future Work}
We have presented a novel approach to link prediction in absence of side information that can effectively exploit the topological contextual information available in a neighborhood of each edge. We have empirically shown that this approach achieves very competitive results compared to other state-of-the-art methods.
In the future, we will investigate how to make use of multiple and heterogeneous information sources when these are available for nodes and edges.
